---
title: "p8105_hw5_yj2688"
output: github_document
---

## Problem 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(ggplot2)
library(patchwork)
set.seed(10)
```

```{r, warning=FALSE, message=FALSE}
files = list.files("./data", pattern = ".csv", all.files = FALSE, 
full.names = FALSE)

long = data.frame(participants = files) %>% 
  mutate(contents = map(participants, ~read.csv(file.path("./data", .)))) %>% 
  separate(participants, into = c("control", "subject_id")) %>% 
  unnest(contents) %>% 
  mutate(control = recode(control, `con` = "control", `exp` = "experiment")) 

spaghetti = long %>% pivot_longer(week_1:week_8,
                                  names_to = "week",
                                  names_prefix = "week_",
                                  values_to = "result") %>% 
  ggplot(aes(x = week, y = result, group = subject_id, color = subject_id)) + 
  geom_path() + 
  facet_grid(~control) + 
  labs(title = "Grouped Results Over Time",
       x = "Week",
       y = "Result") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  viridis::scale_color_viridis(discrete = TRUE)

spaghetti

```

## Problem 2

```{r, warning=FALSE, message=FALSE}
#Importing the homicide file into R
csvurl <- 'https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv'
rawhomicide <- read_csv(url(csvurl), show_col_types = FALSE)

#summarise number of homicides within 51 city_states
homicide <- rawhomicide %>% 
  mutate(city_state = str_c(city,",",state),
         status = case_when(
           disposition == "Closed by arrest" ~ "solved",
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved"
         )) %>%
  select(uid,city_state,reported_date,victim_last,victim_first,victim_race,victim_age,victim_sex,lat,lon,status)
```
The raw homicide data contains 52,179 observations and 12 columns. 7 of them are character variables, 5 of them are numeric variables, and in the numeric variables there is a variable for unique ID and a varible for date. There are 51 city_states. 

```{r, warning=FALSE, message=FALSE}
num_of_hom <- homicide %>%
  group_by(city_state) %>% 
  summarise(total_homicide = n(),
            unsolve = sum(status == "unsolved"))

#using prop.test to estimate proportion of unsolved homicides in Baltimore
balt <- num_of_hom %>%
  filter(city_state == "Baltimore,MD")

estimate <- prop.test(
  x = balt %>% pull(unsolve),
  n = balt %>% pull(total_homicide)) %>% broom::tidy()

#save the output of prop.test as an R object
estimate_proportion <- estimate %>% pull(estimate)
ci_low <- estimate %>% pull(conf.low)
ci_up <- estimate %>% pull(conf.high)

balt_output <- list(
  "proportion_estimate" = estimate_proportion,
  "lower_CI_bound" = ci_low,
  "upper_CI_bound" = ci_up
) %>%
  bind_rows() %>%
  broom::tidy()
save(balt_output, file = "./baltimore_output.RData")
```


```{r, warning=FALSE, message=FALSE}
#prop.test for each city, and pull both porprotion and confidence intervals.

#function
proptest <- function(homcity) {
  city_estimate <- prop.test(
  x = balt %>% pull(unsolve),
  n = balt %>% pull(total_homicide)) 
  return(city_estimate)
}

#test all city
test_city = num_of_hom %>%
  nest(data=-city_state) %>%
  mutate(prop_test = map(data, proptest),
         tidy = map(prop_test, broom::tidy)) %>%
  select(city_state,tidy) %>%
  unnest(tidy) %>%
  select(city_state,estimate,starts_with('con')) %>% 
  arrange(desc(estimate))

head(test_city) %>%
  knitr::kable()
```


```{r, warning=FALSE, message=FALSE}
#Plot for estimate and CIs
test_city %>%
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  ggtitle("Proportion Estimate for Unsolved Homicides In Each City") + 
  xlab("City, State") +
  ylab("Proportion Estimate for Unsolved Homicides") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

##Problem 3

```{r, warning=FALSE, message=FALSE}
#setup elements
set <- rerun(5000, rnorm(n = 30, mean = 0, sd = 5))

#t-test function
ttest <- function(mu = 0) {
  set = tibble(rnorm(n = 30, mean = mu, sd = 5))
  
  output = t.test(set) %>%
    broom::tidy() %>%
    select(estimate, p.value)
  
  output
}

#apply ttest to 5000 samples with mean = 0
same_mean <- expand.grid(mean = 0, iteration = 1:5000) %>%
  mutate(output = map(mean,ttest)) %>% 
  unnest(output)

#apply ttest to 5000 samples with means from 1 to 6
diff_mean <- expand.grid(mean=1:6, iteration = 1:5000) %>%
  mutate(output = map(mean,ttest)) %>%
  unnest(output)

```

```{r, warning=FALSE, message=FALSE}
#find out proportion of times that null is rejected
reject_null <- diff_mean %>%
  filter(p.value<0.05) %>%
  group_by(mean) %>%
  summarise(reject_proportion = sum(p.value<0.5)/5000)

power_plot <- reject_null %>% 
  ggplot(aes(x = mean, y = reject_proportion)) +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  geom_point() + 
  geom_path() +
  xlab("Mean") +
  ylab("Proportion of Rejected Tests") +
  ggtitle("t-test Power in Different Means")

power_plot

#find out average estimate of mean
avg_est <- diff_mean %>% 
  group_by(mean) %>%
  summarise(average_estimate = mean(estimate, na.rm = TRUE))

avg_plot <- avg_est %>%
  ggplot(aes(x = mean, y = average_estimate)) +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  geom_point() + 
  geom_path() +
  xlab("Mean") +
  ylab("Average Estimation") +
  ggtitle("Average Estimation in Different Means")

avg_plot

#find out average estimate of mean in samples that were rejected
reject_and_est <- diff_mean %>%
  filter(p.value<0.05) %>%
  group_by(mean) %>% 
  summarise(reject_proportion = sum(p.value<0.5)/5000, 
            average_estimate = mean(estimate, na.rm = TRUE))
ggplot(data = reject_and_est, aes(x = mean, y = average_estimate)) + 
  geom_line(aes(x = mean, y = average_estimate, col = "red")) + 
  geom_point(aes(x = mean, y = average_estimate, col = "red")) + 
  geom_line(aes(x = mean, y = reject_proportion, col = "green")) +
  geom_point(aes(x = mean, y = reject_proportion, col = "green")) + 
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  xlab("Mean") +
  ylab("Average Estimation") +
  ggtitle("Average Estimation VS. t-test Power in Different Means") + 
  scale_color_manual(labels = c("Test Power", "Average Estimate"), values = c("green", "red"))

```

There is a positive relationship between effect size and power. When effect size increases, the power increases. 

The overall sample average estimation for different means are not equal to the null-rejected average estimation for different means. The overall average estimation is linear and it increase with the sample mean. The estimate when the null is rejected is affected by the test power. 